Q1: Are lake and terrestrial primary productivity coherent?

### 2019-11-29 AnalysisCode/Q1_coherenceSpatialVariation/ms1_analyses.Rmd
thinkPiece R1 and reorganization

analysislakes$lakeinfo<-analysislakes$lakeinfo[!sapply(analysislakes$lakedata, function(x){any(is.na(x))}),]
analysislakes$lakedata<-analysislakes$lakedata[!sapply(analysislakes$lakedata, function(x){any(is.na(x))})]
```

@@

hist(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.2]/pi, main="Accumulated NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
#hist(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvip.ts1<0.2]/pi, main="Maximum NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=5)

@@

hist(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts2<0.2]/pi, main="Accumulated NDVI, long timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
#hist(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvicoh.ts2>0.6]/pi, main="Maximum NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=5)

@@

str(predictors)
hist(predictors$lake_area_ha)
hist(log10(predictors$lake_area_ha))
hist(predictors$lake_perim_meters)
hist(log10(predictors$lake_perim_meters))
table(predictors$nhd_fcode)
table(predictors$hu12_zoneid)
hist(predictors$elevation_m)
hist(predictors$maxdepth)
hist(log10(predictors$maxdepth))
hist(predictors$pct.ag)
hist(log10(predictors$pct.ag))
hist(predictors$chla)
hist(log10(predictors$chla))
hist(predictors$tsi)
table(predictors$tsi.cat)

@@

modvars.accndvi.phist<-modvars.accndvi[modvars.accndvi$accndvip.ts1<0.2,]
modvars.accndvi.philt<-modvars.accndvi[modvars.accndvi$accndvip.ts2<0.2,]

@@

```{r gls modelling, echo=TRUE, cache=FALSE}
#short timescales
gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
                        data=modvars.accndvi,
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
summary(gls.coh.accndvi.st)
suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
print(head(dredge.coh.accndvi.st))

gls.phi.accndvi.st<-gls(cos(accndviphi.ts1) ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
                        data=modvars.accndvi.phist,
                        correlation=corExp(form = ~ nhd_lat + nhd_long)) #remove ftype b/c only lakes
summary(gls.phi.accndvi.st)
suppressWarnings(dredge.phi.accndvi.st<-dredge(gls.phi.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
print(head(dredge.phi.accndvi.st))

#long timescales
gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
                        data=modvars.accndvi,
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
summary(gls.coh.accndvi.lt)
suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
print(head(dredge.coh.accndvi.lt))

gls.phi.accndvi.lt<-gls(cos(accndviphi.ts2) ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
                        data=modvars.accndvi.philt,
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
summary(gls.phi.accndvi.lt)
suppressWarnings(dredge.phi.accndvi.lt<-dredge(gls.phi.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
print(head(dredge.phi.accndvi.lt))
```
That turned up astonishingly little, so now try breaking down by region. 
The regions are: 1) Missouri; 2) Minnesota, Wisconsin, and Michigan; 3) Pennsylvania, New York, Rhode Island, Vermont, New Hampshire, Maine.

```{r gls modeling r1, echo=TRUE, cache=FALSE}
#Region 1: Missouri

modvars.accndvi.r1<-modvars.accndvi[modvars.accndvi$state_name=="Missouri",]
# modvars.accndvi.philt.r1<-modvars.accndvi.philt[modvars.accndvi.philt$state_name=="Missouri",]
# modvars.accndvi.phist.r1<-modvars.accndvi.phist[modvars.accndvi.phist$state_name=="Missouri",]

#short timescales
gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
                        data=modvars.accndvi.r1,
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
summary(gls.coh.accndvi.st)
suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
print(head(dredge.coh.accndvi.st))

#long timescales
gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
                        data=modvars.accndvi.r1,
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
summary(gls.coh.accndvi.lt)
suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
print(head(dredge.coh.accndvi.lt))

@@

```{r gls modeling r2, echo=TRUE, cache=FALSE}
#Region 2: Minnesota, Wisconsin, Michigan

modvars.accndvi.r2<-modvars.accndvi[modvars.accndvi$state_name %in% c("Minnesota","Wisconsin","Michigan"),]

#short timescales
gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
                        data=modvars.accndvi.r2,
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
summary(gls.coh.accndvi.st)
suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
print(head(dredge.coh.accndvi.st))

#long timescales
gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
                        data=modvars.accndvi.r2,
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
summary(gls.coh.accndvi.lt)
suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
print(head(dredge.coh.accndvi.lt))

```
```{r gls modeling r3, echo=TRUE, cache=FALSE}
#Region 2: Minnesota, Wisconsin, Michigan

modvars.accndvi.r3<-modvars.accndvi[modvars.accndvi$state_name %in% c("Pennsylvania","New York","Rhode Island","Vermont","New Hampshire","Maine"),]

#short timescales
gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
                        data=modvars.accndvi.r3,
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
summary(gls.coh.accndvi.st)
suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
print(head(dredge.coh.accndvi.st))

#long timescales
gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
                        data=modvars.accndvi.r3,
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
summary(gls.coh.accndvi.lt)
suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
print(head(dredge.coh.accndvi.lt))

>>>>

analysislakes$lakeinfo<-analysislakes$lakeinfo[!sapply(analysislakes$lakedata, function(x){any(is.na(x))}),]
analysislakes$lakedata<-analysislakes$lakedata[!sapply(analysislakes$lakedata, function(x){any(is.na(x))})]

analysislakes$lakeinfo$tslength<-analysislakes$lakeinfo$end-analysislakes$lakeinfo$start+1
# analysislakes$lakedata<-analysislakes$lakedata[analysislakes$lakeinfo$tslength >= 20]
# analysislakes$lakeinfo<-analysislakes$lakeinfo[analysislakes$lakeinfo$tslength >= 20,]

@@

hist(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.3]/pi, main="Accumulated NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
#hist(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvip.ts1<0.2]/pi, main="Maximum NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=5)

@@

hist(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts2<0.3]/pi, main="Accumulated NDVI, long timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
#hist(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvicoh.ts2>0.6]/pi, main="Maximum NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=5)

@@

str(predictors)
hist(predictors$tslength)
hist(predictors$lake_area_ha)
hist(log10(predictors$lake_area_ha))
hist(predictors$lake_perim_meters)
hist(log10(predictors$lake_perim_meters))
table(predictors$nhd_fcode)
table(predictors$hu12_zoneid)
hist(predictors$elevation_m)
hist(predictors$maxdepth)
hist(log10(predictors$maxdepth))
hist(predictors$pct.ag)
hist(log10(predictors$pct.ag))
hist(predictors$chla)
hist(log10(predictors$chla))
hist(predictors$tsi)
table(predictors$tsi.cat)

@@

modvars.accndvi.phist<-modvars.accndvi[modvars.accndvi$accndvip.ts1<0.3,]
modvars.accndvi.philt<-modvars.accndvi[modvars.accndvi$accndvip.ts2<0.3,]

modvars.accndvi[modvars.accndvi$tslength < 20,]

@@

```{r gls modelling, echo=TRUE, cache=FALSE}
#short timescales
gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
                        data=modvars.accndvi,
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
summary(gls.coh.accndvi.st)

hist(predict(gls.coh.accndvi.st))
plot(predict(gls.coh.accndvi.st), modvars.accndvi$accndvicoh.ts1, ylim=c(0,1), xlim=c(0,1),
     ylab="empirical", xlab="predicted", main="Coherence, short ts")
abline(a=0,b=1)
cor.test(predict(gls.coh.accndvi.st),modvars.accndvi$accndvicoh.ts1)

suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
print(head(dredge.coh.accndvi.st))

modavg.coh.accndvi.st<-model.avg(dredge.coh.accndvi.st, fit=T)
modavg.coh.accndvi.st$importance

hist(predict(modavg.coh.accndvi.st))
plot(predict(modavg.coh.accndvi.st), modvars.accndvi$accndvicoh.ts1, ylim=c(0,1), xlim=c(0,1),
     ylab="empirical", xlab="predicted", main="Coherence, short ts")
abline(a=0,b=1)
cor.test(predict(modavg.coh.accndvi.st),modvars.accndvi$accndvicoh.ts1)

gls.phi.accndvi.st<-gls(cos(accndviphi.ts1) ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
                        data=modvars.accndvi.phist,
                        correlation=corExp(form = ~ nhd_lat + nhd_long)) #remove ftype b/c only lakes
summary(gls.phi.accndvi.st)
suppressWarnings(dredge.phi.accndvi.st<-dredge(gls.phi.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
print(head(dredge.phi.accndvi.st))

#long timescales
gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
                        data=modvars.accndvi,
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
summary(gls.coh.accndvi.lt)
suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
print(head(dredge.coh.accndvi.lt))

gls.phi.accndvi.lt<-gls(cos(accndviphi.ts2) ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
                        data=modvars.accndvi.philt,
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
summary(gls.phi.accndvi.lt)
suppressWarnings(dredge.phi.accndvi.lt<-dredge(gls.phi.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
print(head(dredge.phi.accndvi.lt))
```
Early iterations of this made us wonder of things differed by region, so we tested these relationships broken down into 3 regions.
The regions are: 1) Missouri; 2) Minnesota, Wisconsin, and Michigan; 3) Pennsylvania, New York, Rhode Island, Vermont, New Hampshire, Maine.

```{r gls modeling r1, echo=TRUE, cache=FALSE}
# #Region 1: Missouri
# 
# modvars.accndvi.r1<-modvars.accndvi[modvars.accndvi$state_name=="Missouri",]
# # modvars.accndvi.philt.r1<-modvars.accndvi.philt[modvars.accndvi.philt$state_name=="Missouri",]
# # modvars.accndvi.phist.r1<-modvars.accndvi.phist[modvars.accndvi.phist$state_name=="Missouri",]
# 
# #short timescales
# gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
#                         data=modvars.accndvi.r1,
#                         correlation=corExp(form = ~ nhd_lat + nhd_long))
# summary(gls.coh.accndvi.st)
# suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
# print(head(dredge.coh.accndvi.st))
# 
# #long timescales
# gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
#                         data=modvars.accndvi.r1,
#                         correlation=corExp(form = ~ nhd_lat + nhd_long))
# summary(gls.coh.accndvi.lt)
# suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
# print(head(dredge.coh.accndvi.lt))

@@

```{r gls modeling r2, echo=TRUE, cache=FALSE}
# #Region 2: Minnesota, Wisconsin, Michigan
# 
# modvars.accndvi.r2<-modvars.accndvi[modvars.accndvi$state_name %in% c("Minnesota","Wisconsin","Michigan"),]
# 
# #short timescales
# gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
#                         data=modvars.accndvi.r2,
#                         correlation=corExp(form = ~ nhd_lat + nhd_long))
# summary(gls.coh.accndvi.st)
# suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
# print(head(dredge.coh.accndvi.st))
# 
# #long timescales
# gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
#                         data=modvars.accndvi.r2,
#                         correlation=corExp(form = ~ nhd_lat + nhd_long))
# summary(gls.coh.accndvi.lt)
# suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
# print(head(dredge.coh.accndvi.lt))

```
```{r gls modeling r3, echo=TRUE, cache=FALSE}
# #Region 2: Minnesota, Wisconsin, Michigan
# 
# modvars.accndvi.r3<-modvars.accndvi[modvars.accndvi$state_name %in% c("Pennsylvania","New York","Rhode Island","Vermont","New Hampshire","Maine"),]
# 
# #short timescales
# gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
#                         data=modvars.accndvi.r3,
#                         correlation=corExp(form = ~ nhd_lat + nhd_long))
# summary(gls.coh.accndvi.st)
# suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
# print(head(dredge.coh.accndvi.st))
# 
# #long timescales
# gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
#                         data=modvars.accndvi.r3,
#                         correlation=corExp(form = ~ nhd_lat + nhd_long))
# summary(gls.coh.accndvi.lt)
# suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
# print(head(dredge.coh.accndvi.lt))

### 2019-11-29 AnalysisCode/Q1_coherenceSpatialVariation/ms1_analyses_randforest.Rmd
thinkPiece R1 and reorganization

predictors$log10_lake_area_ha<-log10(predictors$lake_area_ha) #not necessary to transform with random forests
# predictors$log10_lake_perim_meters<-log10(predictors$lake_perim_meters)
# predictors$log10_maxdepth<-log10(predictors$maxdepth)
# predictors$log10_pct.ag<-log10(predictors$pct.ag+1)
# predictors$log10_chla<-log10(predictors$chla)

@@

# cforest.st<-partykit::cforest(accndvicoh.ts1 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + cv.accndvi, 
# #                     data=modvars.accndvi, ntree=20000)
# cforest.st<-party::cforest(accndvicoh.ts1 ~ shoredev + lake_area_ha +  maxdepth + pct.ag + chla + tsi.cat + 
#                              hu4_zoneid + cv.accndvi + pct.wetlands + doc + prcp.normal,
#                     data=modvars.accndvi, controls=cforest_control(ntree=80000))

lwgt<-modvars.accndvi$tslength/mean(modvars.accndvi$tslength)

gam.cohst<-gam(accndvicoh.ts1 ~ s(shoredev) + s(prcp.normal) + s(log10(lake_area_ha)) + s(pct.ag),  weights=lwgt, data=modvars.accndvi, 
               gamma=1.4, na.action = "na.fail")
#dredge.cohst<-dredge(gam.cohst, evaluate=TRUE, m.lim=c(0,5))
#importance(dredge.cohst)
#modavg.cohst<-model.avg(dredge.cohst, fit=T)
summary(gam.cohst)

plot(modvars.accndvi$accndvicoh.ts1,predict(gam.cohst))

topmod.cohst<-gam(accndvicoh.ts1 ~ s(shoredev,k=3) + s(log10(lake_area_ha),k=3) + s(prcp.normal,k=3) + s(pct.ag,k=3), data=modvars.accndvi,
                  gamma=1)
summary(topmod.cohst)

gam.cohlt<-gam(accndvicoh.ts2 ~ s(shoredev,k=3) + s(log10(lake_area_ha),k=3) +  s(maxdepth,k=3) + s(pct.ag,k=3) + 
                 s(chla,k=3) + tsi.cat + hu4_zoneid + s(cv.accndvi,k=3) + s(pct.wetlands,k=3) +  #removed doc because of NAs
                 s(prcp.normal,k=3), data=modvars.accndvi, gamma=1,na.action = "na.fail")
dredge.cohlt<-dredge(gam.cohlt, evaluate=TRUE, m.lim=c(0,5))
importance(dredge.cohlt)
modavg.cohlt<-model.avg(dredge.cohlt, fit=T)

plot(modvars.accndvi$accndvicoh.ts1,predict(modavg.cohlt))

topmod.cohlt<-gam(accndvicoh.ts1 ~ s(pct.wetlands,k=3) + s(cv.accndvi,k=3) + s(prcp.normal,k=3) + s(maxdepth,k=3), data=modvars.accndvi,
                  gamma=1)
summary(topmod.cohlt)

predcoh.st<-predict(cforest.st, newdata=modvars.accndvi,type="response")
#hist(predcoh.st)
#hist(modvars.accndvi$accndvicoh.ts1)
plot(predcoh.st, modvars.accndvi$accndvicoh.ts1, xlab="predicted", ylab="empirical", main="Coherence, short ts",
     xlim=c(0,1), ylim=c(0,1))
abline(a=0,b=1)
cor.test(predcoh.st,modvars.accndvi$accndvicoh.ts1)
varimp.coh.st<-varimp(cforest.st)
print(varimp.coh.st[order(varimp.coh.st, decreasing=T)])

@@

cforest.lt<-party::cforest(accndvicoh.ts2 ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid 
                           + cv.accndvi+ pct.wetlands + doc + prcp.normal, 
                    data=modvars.accndvi, controls=cforest_control(ntree=80000))
predcoh.lt<-predict(cforest.lt, newdata=modvars.accndvi)
# hist(predcoh.lt)
# hist(modvars.accndvi$accndvicoh.ts2)
plot(predcoh.lt, modvars.accndvi$accndvicoh.ts2, xlab="predicted", ylab="empirical", main="Coherence, long st",
     xlim=c(0,1), ylim=c(0,1))
abline(a=0,b=1)
cor.test(predcoh.lt,modvars.accndvi$accndvicoh.ts2)
varimp.coh.lt<-varimp(cforest.lt)
print(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)])

@@

cforest.phi.st<-cforest(cos(accndviphi.ts1) ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + 
                          hu4_zoneid + cv.accndvi+ pct.wetlands + doc + prcp.normal, 
                        data=modvars.accndvi.phist,controls=cforest_control(ntree=40000))
predphi.st<-predict(cforest.phi.st, newdata=modvars.accndvi.phist)
# hist(predphi.st)
# hist(cos(modvars.accndvi.phist$accndviphi.ts1))
plot(predphi.st, cos(modvars.accndvi.phist$accndviphi.ts1), xlab="predicted", ylab="empirical", main="cos(phase), short ts",
     xlim=c(-1,1), ylim=c(-1,1))
abline(a=0,b=1)
cor.test(predphi.st,cos(modvars.accndvi.phist$accndviphi.ts1))
varimp.phi.st<-varimp(cforest.phi.st)
print(varimp.phi.st[order(varimp.phi.st,decreasing=TRUE)])

@@

cforest.phi.lt<-cforest(cos(accndviphi.ts2) ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + 
                          cv.accndvi + pct.wetlands + doc + prcp.normal, 
                        data=modvars.accndvi.philt,controls=cforest_control(ntree=40000))
predphi.lt<-predict(cforest.phi.lt, newdata=modvars.accndvi.philt)
# hist(predphi.lt)
# hist(cos(modvars.accndvi.philt$accndviphi.ts2))
plot(predphi.lt, cos(modvars.accndvi.philt$accndviphi.ts2), xlab="predicted", ylab="empirical", main="cos(phase), short ts",
     xlim=c(-1,1), ylim=c(-1,1))
abline(a=0,b=1)
cor.test(predphi.lt,cos(modvars.accndvi.philt$accndviphi.ts2))
varimp.phi.lt<-varimp(cforest.phi.lt)
print(varimp.phi.lt[order(varimp.phi.lt, decreasing=TRUE)])

>>>>

# predictors$log10_lake_area_ha<-log10(predictors$lake_area_ha) #not necessary to transform with random forests
# predictors$log10_lake_perim_meters<-log10(predictors$lake_perim_meters)
# predictors$log10_maxdepth<-log10(predictors$maxdepth)
# predictors$log10_pct.ag<-log10(predictors$pct.ag+1)
# predictors$log10_chla<-log10(predictors$chla)

@@

# cforest.st<-partykit::cforest(accndvicoh.ts1 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + cv.accndvi, 
#                     data=modvars.accndvi, ntree=20000)
cforest.st<-party::cforest(accndvicoh.ts1 ~ shoredev + lake_area_ha +  maxdepth + pct.ag + chla + tsi.cat + 
                             hu4_zoneid + cv.accndvi + pct.wetlands + doc + prcp.normal,
                    data=modvars.accndvi, controls=cforest_control(ntree=50000,mincriterion = 0.9))
predcoh.st<-predict(cforest.st, newdata=modvars.accndvi,type="response")
#hist(predcoh.st)
#hist(modvars.accndvi$accndvicoh.ts1)
plot(predcoh.st, modvars.accndvi$accndvicoh.ts1, xlab="predicted", ylab="empirical", main="Coherence, short ts",
     xlim=c(0,1), ylim=c(0,1))
abline(a=0,b=1)
cor.test(predcoh.st,modvars.accndvi$accndvicoh.ts1)
varimp.coh.st<-varimp(cforest.st)
print(varimp.coh.st[order(varimp.coh.st, decreasing=T)])

@@

cforest.lt<-party::cforest(accndvicoh.ts2 ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid 
                           + cv.accndvi+ pct.wetlands + doc + prcp.normal, 
                    data=modvars.accndvi, controls=cforest_control(ntree=50000,mincriterion = 0.9))
predcoh.lt<-predict(cforest.lt, newdata=modvars.accndvi)
# hist(predcoh.lt)
# hist(modvars.accndvi$accndvicoh.ts2)
plot(predcoh.lt, modvars.accndvi$accndvicoh.ts2, xlab="predicted", ylab="empirical", main="Coherence, long st",
     xlim=c(0,1), ylim=c(0,1))
abline(a=0,b=1)
cor.test(predcoh.lt,modvars.accndvi$accndvicoh.ts2)
varimp.coh.lt<-varimp(cforest.lt)
print(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)])

@@

cforest.phi.st<-cforest(cos(accndviphi.ts1) ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + 
                          hu4_zoneid + cv.accndvi+ pct.wetlands + doc + prcp.normal, 
                        data=modvars.accndvi.phist,controls=cforest_control(ntree=50000))
predphi.st<-predict(cforest.phi.st, newdata=modvars.accndvi.phist)
# hist(predphi.st)
# hist(cos(modvars.accndvi.phist$accndviphi.ts1))
plot(predphi.st, cos(modvars.accndvi.phist$accndviphi.ts1), xlab="predicted", ylab="empirical", main="cos(phase), short ts",
     xlim=c(-1,1), ylim=c(-1,1))
abline(a=0,b=1)
cor.test(predphi.st,cos(modvars.accndvi.phist$accndviphi.ts1))
varimp.phi.st<-varimp(cforest.phi.st)
print(varimp.phi.st[order(varimp.phi.st,decreasing=TRUE)])

@@

cforest.phi.lt<-cforest(cos(accndviphi.ts2) ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + 
                          cv.accndvi + pct.wetlands + doc + prcp.normal, 
                        data=modvars.accndvi.philt,controls=cforest_control(ntree=50000))
predphi.lt<-predict(cforest.phi.lt, newdata=modvars.accndvi.philt)
# hist(predphi.lt)
# hist(cos(modvars.accndvi.philt$accndviphi.ts2))
plot(predphi.lt, cos(modvars.accndvi.philt$accndviphi.ts2), xlab="predicted", ylab="empirical", main="cos(phase), short ts",
     xlim=c(-1,1), ylim=c(-1,1))
abline(a=0,b=1)
cor.test(predphi.lt,cos(modvars.accndvi.philt$accndviphi.ts2))
varimp.phi.lt<-varimp(cforest.phi.lt)
print(varimp.phi.lt[order(varimp.phi.lt, decreasing=TRUE)])
